Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking

### 2018-06-11 paper.tex
update

    \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{abilene_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{newyork_geni_throughput_e05.eps}
  \end{figure}
    \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{polska_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{di-yuan_geni_throughput_e05.eps}
  \end{figure}
  \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{nobel-us_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{pdh_geni_throughput_e05.eps}
  \end{figure}
  \chapter{Summary}
    \section{conclusion}
    \section{future work}
  \begin{thebibliography}{1}
\bibitem{iperf}
    iPerf, \emph{https://iperf.fr/}.
\bibitem{our}
    Tzu-Wen Chang, Yao-Jen Tang, Ming-Jer Tsai, \emph{Efficient Algorithm for Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks}.

>>>>

    \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{abilene_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{newyork_geni_throughput_e05.eps}
  \end{figure}
    \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{polska_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{di-yuan_geni_throughput_e05.eps}
  \end{figure}
  \begin{figure}[ht]
    \caption{The impact of the switch capacity on the total throughput on GENI.}
	\centering
	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
	  \includegraphics[width=1.0\textwidth]{nobel-us_geni_throughput_e05.eps}
	  \includegraphics[width=1.0\textwidth]{pdh_geni_throughput_e05.eps}
  \end{figure}
  \chapter{Summary}
    \section{conclusion}
    \qquad For implementing a routing algorithm of SDN, GENI is a persuasive environment for experiment compared to simulator like NS-2, mininet, ... . In this thesis, we divided the algorithms into online algorithm and offline algorithm. For each part, we gave a full description about how to implement it in GENI.  Reader could base on this thesis to get a faster way for building their experiment. 
  \begin{thebibliography}{1}
\bibitem{iperf}
    iPerf, \emph{https://iperf.fr/}.
\bibitem{our}
    Tzu-Wen Chang, Yao-Jen Tang, Ming-Jer Tsai, \emph{Efficient Algorithm for Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks}.
